---
title: "My R Project"
author: "Kaya Jakowczuk"
date: "August 6, 2025"
---

![](/phones.jfif){fig-align="center"}

Welcome to my website!! Here, I will be showing off my R portfolio.

I created this website as part of a course at Dominican University. It was created with R and Quarto in RStudio.

Special shout out to Dr. Bob for this awesome summer crash course opportunity.

Special thanks to the CrumpLab which made the template for this website available in github: <https://github.com/CrumpLab/quartoCourseBlog>

..............................................................................................................................................

# Introduction

Questions

1.) Which region has the most hours spent on social media platforms?

2.) What's the most used social media platform and what's the social media addiction score?

Predictions

I predict a positive relationship occurring in which students who live in the United States spend the most hours on Instagram with a social media addiction score falling in between the 8-10 range, with a median score of 8.

Data Source

-   Students' Social Media Addiction: <https://www.kaggle.com/datasets/adilshamim8/social-media-addiction-vs-relationships/data>

# Methods

## Data Source

-   What is the source?

    -   Source: Students' Social Media Addiction

-   How was the data collected?

    -   This data was collected in a one-time online survey administered in the first quarter of the year. Participants are then recruited through their university mailing lists and social-media platforms, ensuring diverse results. This data was collected in 2025.

-   What are the variables included?

| Variable | Description |
|---------------------------------------|---------------------------------|
| Student_ID | Unique respondent identifier |
| Age | Age in years |
| Gender | "Male" or "Female" |
| Academic_Level | High School / Undergraduate / Graduate |
| Country | Country of residence |
| Avg_Daily_Usage_Hours | Average hours per day on social media |
| Most_Used_Platform | Instagram, Facebook, TikTok, etc. |
| Affects_Academic_Performance | Self-reported impact on academics (Yes/No) |
| Sleep_Hours_Per_Night | Average nightly sleep hours |
| Mental_Health_Score | Self-rated mental health (1 = poor to 10 = excellent) |
| Relationship_Status | Single / In Relationship / Complicated |
| Conflicts_Over_Social_Media | Number of relationship conflicts due to social media |
| Addicted_Score | Social Media Addiction Score (1 = low to 10 = high) |

: Key Variables

-   How many records/rows/participants?

    -   There are 13 variables with 705 participants, totaling to 706 rows.

-   Any other relevant information

    -   In this project, country was changed to region to match the various types of countries listed for ease, but left alone as a variable.

    -   Duplicate entries were removed due to the unique Student_ID participants entered in the survey.

    -   This survey was completely anonymous.

## Packages Used

-   Tools

    -   R and RStudio in Posit.Cloud

    -   GitHub for website hosting

    -   ggplots2 package

    -   tidyverse package

    -   Kaggle Data Sets

## Approach

-   Approach

    -   For question 1, I will examine the correlation between Country and Avg_Daily_Usage_Hours.

    -   For question 2, I will examine the correlation between Most_Used_Platform and Addicted_Score.

-   Predictions

    -   I predict that students who live in the Americas spend around six hours on social media platforms.

    -   I predict the most used social media platform to be Instagram with a high social media addiction score of eight.

# Results

### Question 1 - Which region has the most hours spent on social media platforms?

-   Code:

    ```{r}
    #install.packages("ggplot2")
    library(ggplot2)
    library(tidyverse)


    students_social_media_addiction <- read.csv("Students Social Media Addiction.csv")
    region_mapping <- read.csv("all.csv")

    students_social_media_addiction$Country <- gsub(
      "USA",
      "United States of America",
      students_social_media_addiction$Country
    )

    students_social_media_addiction$Country <- gsub(
      "UK",
      "United Kingdom of Great Britain and Northern Ireland",
      students_social_media_addiction$Country
    )

    students_social_media_addiction$Country <- gsub(
      "South Korea",
      "Korea, Democratic People's Republic of",
      students_social_media_addiction$Country
    )

    students_social_media_addiction$Country <- gsub(
      "Russia",
      "Russian Federation",
      students_social_media_addiction$Country
    )

    students_social_media_addiction$Country <- gsub(
      "Netherlands",
      "Netherlands, Kingdom of the",
      students_social_media_addiction$Country
    )

    students_social_media_addiction$Country <- gsub(
      "Vietnam",
      "Viet Nam",
      students_social_media_addiction$Country
    )


    students_social_media_addiction$region <- 
      region_mapping[
        match(students_social_media_addiction$Country, region_mapping$name),
        "region"
      ]

    students_social_media_addiction <- students_social_media_addiction |>
      filter(!is.na(region))


    ggplot(students_social_media_addiction) + 
      stat_summary(
        aes(x = Avg_Daily_Usage_Hours, y = region),
        fun.min = min,
        fun.max = max,
        fun = mean
      ) + labs(
        title = "Average Daily Hours Spent on Platforms by Region"
      )

    # ggsave(filename = "avg_hrs_spent_by_region.png")
    ```

-   In conclusion, the Americas region has the highest average daily usage hours on social media platforms.

### Question 2 - What's the most used social media platform and what's the social media addiction score?

#### Graph 1

-   Code:

```{r}
library(ggplot2)
#install.packages("ggplot2")

students_social_media_addiction <- read.csv("Students Social Media Addiction.csv")

ggplot(
  data = students_social_media_addiction,
  mapping = aes(y = Most_Used_Platform))+ geom_bar(fill = "blue", alpha = 0.5) + labs(
    title = "Most Used Social Media Platform"
  )

#ggsave(filename = "most_used_platform.png")
```

-   In conclusion, Instagram is the most used social media platform.

#### Graph 2

-   Code:

```{r}
library(ggplot2)
#install.packages("ggplot2")

students_social_media_addiction <- read.csv("Students Social Media Addiction.csv")

ggplot(
  data = students_social_media_addiction,
  mapping = aes(y = Most_Used_Platform, x = Addicted_Score)) + geom_boxplot(fill = "blue", alpha = 0.5) + labs(
    title = "Addicted Score vs. Most Used Platform"
  ) 

#ggsave(filename = "addicted_score_vs_platform.png")
```

-   In conclusion, Instagram's social media addiction score is between 5-8, with the highest median score of 7.

# Discussion

-   Overall, my hypothesis is supported and therefore I believe it more. The reason being is that I claimed students living in the United States, so in the Americas region, spend the most hours on social media platforms. Initially, I had Tiktok as my predicted most used platform, but I changed it to Instagram instead since I believe students, like myself, use that platform the most. At first, I predicted that students would fall in the 8-10 range for the social media addiction score on Instagram. This prediction isn't completely wrong, however the score range I predicted was too high and predicted median was one higher than the resulted median.
